Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits

### 2018-11-13 Manuscript_draft/Manuscript_draft.Rmd
changes

Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 (More refs).

@@

>>>>

Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashamn2013 @arceo2016. A general overview of it is that reduces species fitness (REFS). Other general facts... Quantity of foreign pollen that arrives...

Mention invasive species in this paragraph

Few studies have tried to understand how relatedness is involved in the hp effect but generally

Until our knowledge ....

Rescue from here the useful things:

@@

what is closely related? same genus? Just that right, the rest is far related?

I would like to add that the experiments focus on two proxies of effect prezygotic and postzygotic. Why focus on postzygotic? Is the final stage where we can see the effect. Further studies should also study germination rates.

### 2018-11-13 Manuscript_draft/Manuscript_draft.tex
changes

In natural systems plant species normally coexist and share their floral
visitors with other species Bascompte et al. (2003). This pollinator
sharing from the plant perspective at the pre-pollination stage can be
negative due to competition Pauw (2013) or positive due to facilitation
Carvalheiro et al. (2014). Once, the floral visitor has arrived to the
flower, pollen deposition on the stigma can take place and hence ovule
fertilization. An increasing number of visits generally correlates with
higher chances of fertilization (Refs). However this is not always the
case, among these possible flower visitors we find also nectar robbers
and pollen thiefs (Refs) and the quality of pollen that is deposited on
the stigma is also highly relevant to the pollination succes (Refs).
Moreover, other less studies issues in the pollination process are
conspecific pollen loss and the arrival of foreign pollen which can have
important detrimental effects for the species fitness Morales and
Traveset (2008) (More refs).

@@

Recent important studies have advanced in the ecological importance of
heterospecific pollen effect Morales and Traveset (2008) (More refs).

>>>>

In natural systems plant species normally coexist and share their floral
visitors with other species Bascompte et al. (2003). This pollinator
sharing from the plant perspective at the pre-pollination stage can be
negative due to competition Pauw (2013) or positive due to facilitation
Carvalheiro et al. (2014). Once, the floral visitor has arrived to the
flower, pollen deposition on the stigma can take place and hence ovule
fertilization. An increasing number of visits generally correlates with
higher chances of fertilization (Refs). However this is not always the
case, among these possible flower visitors we find also nectar robbers
and pollen thiefs (Refs) and the quality of pollen that is deposited on
the stigma is also highly relevant to the pollination succes (Refs).
Moreover, other less study issues in the pollination process are
conspecific pollen loss and the arrival of foreign pollen which can have
important detrimental effects for the species fitness Morales and
Traveset (2008) (More refs).

@@

Recent important studies have advanced in the ecological importance of
heterospecific pollen effect Morales and Traveset (2008)
({\textbf{???}}) Arceo-Gómez and Ashman (2016). A general overview of it
is that reduces species fitness (REFS). Other general facts\ldots{}
Quantity of foreign pollen that arrives\ldots{}

Mention invasive species in this paragraph

Few studies have tried to understand how relatedness is involved in the
hp effect but generally

Until our knowledge \ldots{}.

Rescue from here the useful things:
